Models

### 2021-10-19 analysis/05_model_metrics.Rmd
Get contrasts for slopes not for intercept differences.

  if(!model_id %in% c("base", "base_dur", "base_srt")){
    level_slopes <- get_fixed_slopes(metric = metric_name, model = fit$result, model_id = model_id, model_data = fit_data) %>%
      mutate(effect = "group_slope", group = model_id) %>%
      rename(std.error = SE, estimate = year_scaled.trend, term = model_id)

    int_contrasts <- get_int_contrasts(metric = metric_name, model = fit$result, model_id = model_id, model_data = fit_data) %>%
      mutate(group = model_id, effect = "contrast") %>%
      rename(std.error = SE, statistic = t.ratio, term = contrast) %>%
      select(-year_scaled)

    df <- tidy(fit$result) %>% 
      bind_rows(level_slopes, int_contrasts) %>%
      mutate(metric = metric_name, model = list(fit$result), model_id = model_id, warning = ifelse(length(fit$warnings) == 0, NA, fit$warnings))
  }else{
  tidy(fit$result) %>%
   mutate(metric = metric_name, model = list(fit$result), model_id = model_id, warning = ifelse(length(fit$warnings) == 0, NA, fit$warnings))
  }
}

get_int_contrasts <- function(metric, model, model_id, model_data){
  formula <- paste("pairwise ~", model_id, "| year_scaled")
  emm <- emmeans(model,  mode = "satterth", lmerTest.limit = 20105, specs = as.formula(formula), data = model_data)

  return(as_tibble(emm$contrasts))
}

get_fixed_slopes <- function(metric, model, model_id, model_data){
  formula <- paste("~", model_id)
  fit_trends <- emtrends(model, specs = as.formula(formula), var="year_scaled",  mode = "satterth", lmerTest.limit = 20105, data = model_data) %>% as_tibble()

>>>>

  if(!model_id %in% c("base", "base_dur", "base_srt")){
    slopes <- get_fixed_slopes(metric = metric_name, model = fit$result, model_id = model_id, model_data = fit_data)

    group_slopes <- as_tibble(slopes$emtrends) %>%
      mutate(effect = "group_slope", group = model_id) %>%
      rename(std.error = SE, estimate = year_scaled.trend, term = model_id)

    slope_constrasts <- as_tibble(slopes$contrasts) %>%
      mutate(effect = "contrast", group = model_id) %>%
      rename(std.error = SE, term = contrast, statistic = t.ratio)

    df <- tidy(fit$result) %>% 
      bind_rows(group_slopes, slope_constrasts) %>%
      mutate(metric = metric_name, model = list(fit$result), model_id = model_id, warning = ifelse(length(fit$warnings) == 0, NA, fit$warnings))
  }else{
  tidy(fit$result) %>%
   mutate(metric = metric_name, model = list(fit$result), model_id = model_id, warning = ifelse(length(fit$warnings) == 0, NA, fit$warnings))
  }
}

get_fixed_slopes <- function(metric, model, model_id, model_data){
  formula <- paste("pairwise", "~", model_id)
  fit_trends <- emtrends(model, specs = as.formula(formula), var="year_scaled",  mode = "satterth", lmerTest.limit = 20105, data = model_data)

### 2021-10-19 analysis/exporatory_scripts/problem_model.Rmd
Get contrasts for slopes not for intercept differences.

#fixed effects contrasts
fit_fixed <- lmer(formula = "value ~ year_scaled*taxa + (year_scaled|study_id/rarefyID)", data = test_data)
m_emm <-  emmeans(fit_fixed,  mode = "satterth", lmerTest.limit = 20105, pairwise ~ taxa | year_scaled)

fit_cont <- as_tibble(m_emm$contrasts)
fit_trends <- emtrends(fit_fixed, ~ taxa, var="year_scaled",  mode = "satterth", lmerTest.limit = 20105) %>% as_tibble()

>>>>

#fixed effects contrasts
fit_fixed <- lmer(formula = "value ~ year_scaled*taxa + (year_scaled|study_id/rarefyID)", data = test_data)

#intercept contrasts
m_emm <-  emmeans(fit_fixed,  mode = "satterth", lmerTest.limit = 20105, pairwise ~ taxa | year_scaled)
fit_cont <- as_tibble(m_emm$contrasts)

#slope contrasts and within group slope estimates
fit_trends <- emtrends(fit_fixed, pairwise ~ taxa, var="year_scaled",  mode = "satterth", lmerTest.limit = 20105) %>% as_tibble()
